\documentclass{article}

\input{misc/packages}
\graphicspath{{./img/}}
\input{misc/macros}

\title{Individual hand-in for first check-in session %
	\footnote{%
        \tobedeleted{\newline %
        The submitted document must keep the structure presented in this template. \\ %
        Limitation on the length of content are stated in red. \\ %
	The supporting text, which is marked in red, must be removed. \\ %
	Finally, remember to submit only the pdf and to change the file name to: \\ %
	``\texttt{<Group Number>\char`_<Student Username>\char`_<Hand-in Number>.pdf}'', e.g., %
	\texttt{XX\char`_pate\char`_1.pdf}}} %
	\\[10pt] %
	\normalsize{[v26.1]}}

\date{\today}
\begin{document}
\maketitle

\vfill
\input{tex/team}
\newpage





\section{Reflect on one main point you learned in Sprints 1–2. This must be stated as an educational observation related to the use of Scrum or other work practices (e.g., what did you learn, how). Your reflection must include at least one concrete reference to something that happened in your team (e.g., a backlog item, a PR or commit, a sprint goal, or a note from a retrospective or TA/coach feedback).}
\label{sec:actual}

\tobedeleted{Suggested length half page.\\For instance: \textbf{Releasing tension.} I learned how laughter can be an effective technique to diffuse tension during a meeting. During retro 1, a flying donkey entered the room when we were stuck arguing on XYZ, we all saw it, it generated a laughter that released the tension of the room. After that, we somehow went back to being respectful of each others' opinion. Even though in this case I can say that the laughter is what helped us, I do not believe laughter would always fix these situations. In the future, I will try to take notes of when the tension raises and try to see whether a `joke' can help returning the amazing team we can be.}

\section{During the experience exchange or community of practice sessions (MSc), (1) how has my active participation benefited others and (2) what did I discuss with others that helped me?}
\label{sec:exchange}
\tobedeleted{Suggested length half page.}
\tobedeleted{Based on your participation in the experience exchange (or Community of Practice for MSc students), describe:}
\begin{itemize}
    \item \tobedeleted{one topic, challenge, or question you discussed with others, and}
    \item \tobedeleted{what insight, feedback, or example you received that helped you.}
\end{itemize}

\tobedeleted{Include at least one concrete connection to your team’s work (e.g., a practice you changed, a story you refined differently, or a tool you adopted).}





\end{document}












