\documentclass{article}

\input{misc/packages}
\graphicspath{{./img/}}
\input{misc/macros}

\title{Individual hand-in for second check-in session %
	\footnote{%
        \tobedeleted{\newline %
        The submitted document must keep the structure presented in this template. \\ %
        Limitation on the length of content are stated in red. \\ %
	The supporting text, which is marked in red, must be removed. \\ %
	Finally, remember to submit only the pdf and to change the file name to: \\ %
	``\texttt{<Group Number>\char`_<Student Username>\char`_<Hand-in Number>.pdf}'', e.g., %
	\texttt{XX\char`_pate\char`_2.pdf}}} %
	\\[10pt] %
	\normalsize{[v26.1]}}

\date{\today}
\begin{document}
\maketitle

\vfill
\input{tex/team}
\newpage

\section{Reflect on one main point you learned in Sprints 3–4. This must be stated as an educational observation related to Scrum or other work methods (e.g., what did you learn, how). Include at least one reference to something concrete from your team’s work during these sprints (e.g., a backlog item, PR, sprint goal, retro note, or interaction with the PO/SM).}
\label{sec:actual}

\tobedeleted{Suggested length half page.\\ For instance: \textbf{Releasing tension.} I learned how laughter can be an effective technique to diffuse tension during a meeting. During retro 1, a flying donkey entered the room when we were stuck arguing on XYZ, we all saw it, it generated a laughter that released the tension of the room. After that, we somehow went back to being respectful of each others' opinion. Even though in this case I can say that the laughter is what helped us, I do not believe laughter would always fix these situations. In the future, I will try to take notes of when the tension raises and try to see whether a `joke' can help returning the amazing team we can be.}



\section{During the experience exchange or community of practice sessions (MSc), (1) how has my active participation benefited others and (2) what did I discuss with others that helped me?}
\label{sec:exchange}
\tobedeleted{Suggested length half page.}
\tobedeleted{Based on your participation to the experience exchange (or Community of Practice for MSc students), describe:}
\begin{itemize}
    \item \tobedeleted{how your participation contributed to others, and }
    \item \tobedeleted{what you learned from others that influenced your work in Sprints 3–4.}
\end{itemize}

\tobedeleted{Include at least one concrete connection reference to something in your project that this discussion affected.}


\end{document}












