\documentclass{article}

\input{misc/packages}
\graphicspath{{./img/}}
\input{misc/macros}

\title{Individual hand-in for the exam session %
	\footnote{%
        \tobedeleted{\newline %
        The submitted document must keep the structure presented in this template. \\ %
        Limitation on the length of content are stated in red. \\ %
	The supporting text, which is marked in red, must be removed. \\ %
	Finally, remember to submit only the pdf and to change the file name to: \\ %
	``\texttt{<Group Number>\char`_<Student Username>\char`_<Hand-in Number>.pdf}'', e.g., %
	\texttt{XX\char`_pate\char`_3.pdf}}} %
	\\[10pt] %
	\normalsize{[v26.1]}}
 
\date{\today}
\begin{document}
\maketitle

\nocite{2001:manifesto}

\vfill
\input{tex/team}
\newpage


\section{Tasks}
\begin{itemize}
    \item Execute the test at \url{https://www.scrum.org/open-assessments/scrum-open}.
    \item Percentage: 76.7\% 
    \item "When does a Developer become the sole owner of an item on the Sprint Backlog?" - I just thought of this question differently than what was intended. In my mind it makes sense to delegate taskes out to different people so the developers know who is working on it.
\end{itemize}


\section{Reflect on one main point you learned in the last two sprints. This must be stated as an educational observation related to Scrum or other work practices (e.g., what did you learn, how). Include at least one concrete reference to an artifact from Sprints 5–6 (e.g., backlog item, PR/commit, sprint event, retro note, TA/coach feedback).}
\label{sec:actual}

I learned that it can be hard to communicate over text, and that ones intentions might not be so clearly defined over text. I had an incident were I reviewed a pr and the author of the pr read the reviewed as me yelling at them. This caused a bit of drama and was on me as I should have communicated better.

I also learned that it might be a good idea for when multiple people review a pr together that they then add a little comment telling the author who reviewed it. This was because I had made a few small changes that I felt was ignored, since it looked like nobody reviewed it. I latter learned that multiple people had reviewed it together but was not transparent about it. When I learned that I felt much better since I learned that I was not ignored



\section{During the experience exchange or community of practice sessions (MSc), (1) how has my active participation benefited others and (2) what did I discuss with others that helped me?}
\label{sec:exchange}
The biggest thing that I learned was that everybody else felt like they could not deliver the finished product that the PO's wanted. This was nice since there were a lot less stress about not finishing a complete product. 
A complete product does not mean that we have nothing to show. It just mean that the ideal dream product could not be finished

\section{Final reflections on the project and learning}

\subsection{Early sprints}
That was not much that surprised me in the first two sprints. But I learned that to many meetings to close to each other leads to inefficient work and meetings.
As mentioned in handin 1 we used to meeting on Tuesdays, Wednesdays and Thursdays but we found out that did not work each day on the project, do to other priorities like other classes. 
To fix the issue we moved the daily scrum meetings to be Monday, Wednesdays and Fridays. Where Fridays are canceled in the last week of the sprint where we have our review and retrospective on Thursdays.
\subsection{Middle sprints}
during the middle of the project we realized that our architecture of the code base was bad, so we decided to refactor our to follow the \href{https://en.wikipedia.org/wiki/Model-view-presenter}{MVP pattern}. The major part of the refactor was done in pull request \#46.
We also had the issue about people not looking at pull requests. As mentioned in handin 2 we tried to solve this by adding a "In Review" field on our kanban board. This field is a subfield of "In Progress". With this field we hoped that it would aid in transparency.
The "In Review" field partially worked. This was due to many of our pr's not being an entire item, because we decided to work more trunk based.
\subsection{Late sprints}
During the later sprints I had an issue with communication as mentioned above and below.
I also had a exam on the 18th of May so I put the project on the backburner in the last sprint.
\subsection{Collaboration and teamwork}
The biggest conflict I was a part of and one I regret was the one mentioned in section \ref{sec:actual}.\\
I had in the past worked on a view switcher between two sub parts of our program. At one point it was changed to work differently. While testing i could not get the new version to work, so I reverted it back to the original. In a latter pr the switcher was changed again, and could not see the reason for why so in the review I wrote:

\say{Looks somewhat good. But Why is the table view deleted???? And why the hate for my functional switch\_view() method and replace it for something that does not work properly???}

On later retrospective I realized that what I wrote was poorly formulated and overly negative. 
This caused the author to feel like I yelled at them, and I probably accidentally did.
We solved the issue by me apologizing for my rude comment. 
This was probably the biggest regret of the I have of the project.
\subsection{Scrum/SE practice}
Throughout the project we have adapted our workflow. The biggest changes we have made was to move the time of our daily scrum meetings and making the "In Review" field 

\newpage
\bibliographystyle{plain}
\bibliography{misc/cite}

\end{document}
