\documentclass{article}

\input{misc/packages}
\graphicspath{{./img/}}
\input{misc/macros}

\title{Scrum Simulation %
	\normalsize{[v26.1]}}

\date{\today}
\begin{document}
\maketitle


\vfill
\input{tex/team}
\newpage



\section{After the Scrum simulation}
\subsubsection*{Tasks}
\begin{itemize}
    \item Execute the test at \url{https://www.scrum.org/open-assessments/scrum-open}.
    \item Percentage: 70\% 
    \item "When does the next Sprint begin?"
        Here I answered that it started after the next Sprint Planning but was surprised that it begins immediately after

        "Who is required to attend the Daily Scrum?"
        I Thought that the Scrum Master was supposed to attend the Daily Scrum
\end{itemize}



\subsubsection*{What are the main points I learned through the simulation?}
\begin{itemize}
    \item In short time frame, 30 min per sprint, Scrum is wasteful 
    \item It is hard to meet the demand in 4+4 min 
    \item It was hard to estimate when we did not know the work time 
\end{itemize}

\subsubsection*{Share overall observations about your experience as a participant of the simulation.}

I did not like the LEGO scrum simulation because it was a stressful event. 
We could not use our estimates since they were created with wrong assumptions and we did not have the time to re-estimate.
It was hard to build anything with a 4+4 minutes work with a 2 min meeting.
In the simulation, because of the time limit, every meeting, Daily Scrum, Scrum- Retrospective and Planning, seemed wasteful and stressful.
It also was a little hard to work with a split PO since she needed to be at both Scrum teams.
This with the limited time frame further added to the stressfulness of the event.
A problem with the event was when we slightly ignored Scrum we seemed to get work done.
This I see more as a problem with us only having 4+4 minutes to build and not representative of Scrum.
Because of this I do not think there is much, if something at all, I can take away from the event.

\end{document}
